---
title: "tarot0624.test"
author: "Noah Carlos"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## library

```{r}
library(jsonlite)
library(tidyverse)
library(dplyr)
library(bslib)
library(bsicons)
library(htmlwidgets)
library(shiny)

```

## Read JSON

```{r}
rw.json <- fromJSON("/Users/noahcarlos/Documents/R_Studio/tarot.0624/tarot/data/card_data.json")

rw.json

```

## Establish Base

```{r}
#BASE

rw.df <- rw.json$cards

name.rwdf <- rw.df%>%
  select(name, type, everything())

rw.df


```

## Creating rw.full which includes reversed card draws

```{r}

names_r <- paste(name.rwdf$name, "Reversed", sep=" ")
name_short_r <- paste(name.rwdf$name_short, "R", sep="")

rw.reversed <- name.rwdf %>%
  select(name, meaning_rev, name_short) %>%
  mutate(name = names_r,
         name_short = name_short_r)

colnames(rw.reversed) <- c('name', 'meaning')

rw.up <- name.rwdf %>%
  select(name, meaning_up, name_short)
  
colnames(rw.reversed) <- c('name', 'meaning', 'name_short')
colnames(rw.up) <- c('name', 'meaning', 'name_short')

#Merge dfs

rw.full <- rbind(rw.up, rw.reversed)

rw.full



```

Adding name_short column to use for image retrieval

```{r}
# creating column name_short
name_short <- name.rwdf$name_short


```

## Playing with random selector

```{r}
pdraw3 <- slice_sample(rw.full, n=3)

pdraw3
```

Creating random selector function for $k$ cards.

```{r}
k_cardpull <- function(deck, k){
  current_pull <- data.frame(slice_sample(deck ,n = k))
  return(current_pull)
}
```

```{r}
# calling two variables

# test_var <- k_cardpull(rw.full, k=3)

# calling two variables

# test_var[1,1]
# test_var[1,2]


# successfully called the name and meaning columns
# now considering how to best process it in shiny
# renderText to output dialogue, etc.


name.past <- test_var[1,1]
meaning.past <- test_var[1,2]
script.past1 <- "This is what the past card can be highlighting in your life..."
script.past2 <- "Is this card highlighting anything signicant that influenced your past?"

name.present <- test_var[2,1]
meaning.present <- test_var[2,2]
script.present1 <- "This is what the present card can be highlighting in your life..."
script.present2 <- "Does this card strike close to home for you right now?"


name.future <- test_var[3,1]
meaning.future <- test_var[3,2]
script.future1 <- "This is what the future card can be highlighting in your life..."
script.future2 <- "Can you see any ways this may relate to your past situations?"


name.future
meaning.future
script.future1
script.future2
```

```{r}
# test name_split

# determining the necessity of this function 

names_split <- function(deck){
  return(deck[,1])
}

test_names <- names_split(test_var)

test_names[1]
test_names[2]
test_names[3]

```

# Building out inner tarot reading elements. Creating containers for each card. Functions to create the output for each card, etc

## Past, Present, Future read_type

Creating Scripts for Reading -> Card Function
```{r}
# names and scripts for card creation

name.past <- test_var[1, 1]
meaning.past <- test_var[1, 2]
script.past1 <- "This is what the past card can be highlighting in your life..."
script.past2 <- "Is this card highlighting anything signicant that influenced your past?"

name.present <- test_var[2, 1]
meaning.present <- test_var[2, 2]
script.present1 <- "This is what the present card can be highlighting in your life..."
script.present2 <- "Does this card strike close to home for you right now?"


name.future <- test_var[3, 1]
meaning.future <- test_var[3, 2]
script.future1 <- "This is what the future card can be highlighting in your life..."
script.future2 <- "Can you see any ways this may relate to your past situations?"



```





Card Function
```{r}

# past_output function
past_output <- function(current_card) {
  layout_column_wrap(
    width = '100%',
    # height = 300,
    card(
      full_screen = TRUE,
      card_header("Past", style = 'font-size:24px; font-weight = bold;'),
      card_body(
        style = "font-style: italic;",
        "This is what the past card can be highlighting in your life...",
        tags$div(style = "margin-bottom: 10px;")
      ),
      
      
      card_title(current_card[1, 1], style = 'font-size:16px; font-weight = bold;', tags$div(style = "margin-bottom: 10px;")),
      card_header(
        paste(current_card[1, 2]),
        style = 'font-size16px;',
        tags$div(style = "margin-bottom: 10px;")
      ),
      
      card_body(
        style = "font-style: italic;",
        "Is this card highlighting anything signicant that influenced your past?",
        tags$div(style = "margin-bottom: 10px;")
      ),
    ),
  )
}

present_output <- function(current_card) {
  layout_column_wrap(
    width = '100%',
    # height = 300,
    card(
      full_screen = TRUE,
      card_header("Present", style = 'font-size:24px; font-weight = bold;'),
      card_body(
        style = "font-style: italic;",
        script.present1,
        tags$div(style = "margin-bottom: 10px;")
      ),
      
      
      card_title(current_card[2, 1], style = 'font-size:16px;', tags$div(style = "margin-bottom: 10px;")),
      card_header(
        paste(current_card[2, 2]),
        style = 'font-size16px; font-weight = bold;',
        tags$div(style = "margin-bottom: 10px;")
      ),
      
      card_body(
        style = "font-style: italic;",
        script.present2,
        tags$div(style = "margin-bottom: 10px;")
      ),
    ),
  )
}

future_output <- function(current_card) {
  layout_column_wrap(
    width = '100%',
    # height = 300,
    card(
      full_screen = TRUE,
      card_header("Future", style = 'font-size:24px; font-weight = bold;'),
      card_body(
        style = "font-style: italic;",
        script.future1,
        tags$div(style = "margin-bottom: 10px;")
      ),
      
      
      card_title(current_card[3, 1], style = 'font-size:16px;', tags$div(style = "margin-bottom: 10px;")),
      card_header(
        paste(current_card[3, 2]),
        style = 'font-size16px; font-weight = bold;',
        tags$div(style = "margin-bottom: 10px;")
      ),
      
      card_body(
        style = "font-style: italic;",
        script.future2,
        tags$div(style = "margin-bottom: 10px;")
      ),
    ),
  )
}







```




```{r}



past_output(test_var)
present_output(test_var)
future_output(test_var)


```

