---
title: "tarot0624.test"
author: "Noah Carlos"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## library
```{r}
library(jsonlite)
library(tidyverse)
library(dplyr)
library(bslib)
```
## Read JSON
```{r}

# imac
rw.json <- fromJSON("/Users/home/Documents/R Studio/tarot.0624/card_data.json")

rw.json

```





## Establish Base

```{r}
#BASE

rw.df <- rw.json$cards

name.rwdf <- rw.df%>%
  select(name, type, everything())

rw.df


```


## Creating rw.full which includes reversed card draws
```{r}

names_r <- paste(name.rwdf$name, "Reversed", sep=" ")
name_short_r <- paste(name.rwdf$name_short, "R", sep="")

rw.reversed <- name.rwdf %>%
  select(name, meaning_rev, name_short) %>%
  mutate(name = names_r,
         name_short = name_short_r)

colnames(rw.reversed) <- c('name', 'meaning')

rw.up <- name.rwdf %>%
  select(name, meaning_up, name_short)
  
colnames(rw.reversed) <- c('name', 'meaning', 'name_short')
colnames(rw.up) <- c('name', 'meaning', 'name_short')

#Merge dfs

rw.full <- rbind(rw.up, rw.reversed)

rw.full



```

Adding name_short column to use for image retrieval
```{r}
# creating column name_short
name_short <- name.rwdf$name_short


```

## Playing with random selector
```{r}
pdraw3 <- slice_sample(rw.full, n=3)

pdraw3
```

Creating random selector function for $k$ cards.
```{r}
k_cardpull <- function(deck, k){
  current_pull <- data.frame(slice_sample(deck ,n = k))
  return(current_pull)
}
```


```{r}
# calling two variables

test_var <- k_cardpull(rw.full, k=3)

# calling two variables

test_var[1,1]
test_var[1,2]

# successfully called the name and meaning columns
# now considering how to best process it in shiny
# renderText to output dialogue, etc.


# name.past <- test_var[1,1]
# meaning.past <- test_var[1,2]
# script.past <-



# name.present
# name.future
# 
# meaning.past
# meaning.present
# meaning.future
# 
# script.past
# script.present
# script.future



```


```{r}
# test name_split

names_split <- function(deck){
  return(deck[,1])
}

test_names <- names_split(test_var)

test_names[1]
test_names[2]
test_names[3]

```








# Building out inner tarot reading elements. Creating containers for each card. Functions to create the output for each card, etc

## Past, Present, Future read_type








